### 2015-11-19 AssignmentVI/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 1 ist fertig; vielleicht nochmal drüberschauen ob du da mit mir übereinstimmst

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$ (7)\\\hline   %add here Complete number of points ---------------------------
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

@@

\subsection*{}
The profile as a PSWM for the given MSA would look like table \ref{tab:pswm}.

@@

>>>>

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$ (6)\\\hline   %add here Complete number of points ---------------------------
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

@@

\subsection*{(a)}
The profile as a PSWM for the given MSA would look like table \ref{tab:pswm}.

@@

\subsection*{(b)}
\subsubsection*{i. Compute the probability that S[1...4] contains P = GT without substitutions.}
There are three different outcomes for this result.

\begin{align}
 p_1 &: S[1] = G\textrm{ and }S[2] =T \nonumber \\
 p_2 &: S[2] = G\textrm{ and }S[3] =T \nonumber \\
 p_3 &: S[3] = G\textrm{ and }S[4] =T \nonumber 
\end{align}

\noindent Since all $S[i]$s are independent of each other, we simple multiply all probabilities for 
each $S[i]$.

\begin{align}
 P(p_1) &= \frac{1}{4} * \frac{1}{4} * 1 * 1 = \frac{1}{16} \nonumber \\
 P(p_2) &= 1 * \frac{1}{4} * \frac{1}{4} * 1 = \frac{1}{16} \nonumber \\
 P(p_3) &= 1 * 1 * \frac{1}{4} * \frac{1}{4} = \frac{1}{16} \nonumber 
\end{align}

\noindent Where $\frac{1}{4}$ is the probability to choose G or C, respectively, and $1$ is the 
probability to choose any character from the alphabet. All three outcomes would fulfill the task, 
so we simply sum up all probabilities:

\begin{equation}
 P(\textrm{S[1...4] contains GT}) = P(p_1) + P(p_2) + P(p_3) = \frac{3}{16} \nonumber
\end{equation}

\subsubsection*{ii. Compute the probability that S[1...6] contains P = AAA with at most one substitution.}
There are three different possible outcomes for P to appear at position 1:

\begin{align}
 S[1...3] &= YAA \nonumber \\
 S[1...3] &= AYA \nonumber \\
 S[1...3] &= AAY \nonumber 
\end{align}

\noindent Each of this possibilities has the probability $\frac{1}{16}$. Since we have four different 
start positions (1,2,3 and 4) and for each position three different outcomes, the final probability 
is:

\begin{equation}
 P(\textrm{S[1...6] contains AAA}) = 4 * 3 * \frac{1}{16} = \frac{3}{4} \nonumber
\end{equation}
